---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Tianyu Wu"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
covid_data_race |> 
  filter(state == "AK") |> 
  ggplot(aes(x = date, y = White_count, color = count_type)) + geom_line()
```
I made a line plot with "covid_date_race" data set, it describes how many covid cases, deaths, and hosp in White people as time goes on. The line of cases has large slope, and the line of deaths and hosp nearly close to zero compare with the line of cases.

2. Are there any conclusions you can draw?

The difference between the count of deaths and hosp with the count of cases are growing larger as time goes on. So cases are increasing expoentially, however, the count of death and hosp has relatively less growth.

3. What were you not able to do due to not having the R knowledge?

I am not able to compare different races count with each other in one plot.

4. What other data would be useful to better understand this data?

"covid_data_orig" is also useful to present the count of cases, deaths, and hosp in White.
